Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-03-29 ident_manu.tex
better schematic added

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Tue Mar 28 14:41:10 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/e933435a9f4d7e068be7e4cc2ed6c72de4df0fb7}{e933435a9f4d7e068be7e4cc2ed6c72de4df0fb7}}

@@

% model schematic
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figs/mod_schem.png}
\caption{Conceptual representation of biogeochemical components for \ac{do} and carbon dioxide modelled in \ac{cgem} (complete equations \citealt{Eldridge10}). FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}
\label{fig:mod_schem}
\end{figure}

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Tue Mar 28 17:29:18 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/55035672775b152721843109c2926082eceeba21}{55035672775b152721843109c2926082eceeba21}}

@@

% model schematic
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figs/mod_schem.pdf}
\caption{Conceptual representation of biogeochemical components modelled in \ac{cgem} (complete equations \citealt{Eldridge10}). FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}
\label{fig:mod_schem}
\end{figure}
